---
title: "NHS-R Template Title"
subtitle: "NHS-R Template Subtitle"
author: "Author Name"
institute: "Author Institute"
date: "Presentation Date"
output:
  xaringan::moon_reader:
    css: 
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r", "css", "yaml"]
      countIncrementalSlides: true
      ratio: "16:9"
    includes:
      after_body: [css/insert-logo.html]
---
class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, center, middle, hide-logo

# This is the inverse slide

## Often used for transitions

---

# Hello World (Option #4)

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>
- Click the `Knit` button to compile it;
- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides.

.footnote[
[1] This is one example of a footnote.

[2] And this is another.
]

---

# Code highlighting

.pull-left[
An example of using the trailing comment `#<<` to highlight lines:

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````
]

.pull-right[
Output:

```{r tidy=FALSE, eval=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
]
