---
title: "NHS-R Theme &mdash; Presentation title"
subtitle: "Presentation subtitle"
author: "Author Name"
institute: "NHS Organisation"
date: "Presentation Date"
output:
  xaringan::moon_reader:
    css: 
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs
    seal: false
    self_contained: true
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "4:3"
---
class: title-slide, left, bottom
```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(nhsrtheme)
library(xaringanExtra)
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300,
               dev.args = list(type = "cairo"))

# uncomment the following lines if you want to use the NHS-R theme colours by default
# scale_fill_continuous <- partial(scale_fill_nhs, discrete = FALSE)
# scale_fill_discrete <- partial(scale_fill_nhs, discrete = TRUE)
# scale_colour_continuous <- partial(scale_colour_nhs, discrete = FALSE)
# scale_colour_discrete <- partial(scale_colour_nhs, discrete = TRUE)
```

```{r echo=FALSE}
xaringanExtra::use_logo(
  image_url = "img/logo-nhs-blue.png",
  exclude_class = c("title-slide", "inverse", "hide-logo")
)
```


# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, middle, center

# An inverse slide

### Often used for transitions

Links on an inverse slide would look like<br/>[this one leading to information about logos](#logos)

---
# Bullets and text color

--

* first point

--

* second point

--

* third point

--

-----

You can emphasize text with color:

* .blue[Blue]
* .green[Green]
* .pink[Pink]
* .red[Red]
* .warmyellow[Warm Yellow]

--

And make it **bold** or _italicized_ using Markdown:

* .blue[**Bold** or _italicized_]
* .green[**Bold** or _italicized_]
* .pink[**Bold** or _italicized_]
* .red[**Bold** or _italicized_]
* .warmyellow[**Bold** or _italicized_]

---
# Tables and quotes

### Table

```{r}
knitr::kable(head(iris), format = 'html')
```

### Quote

> This is what a quote looks like.

---
# Line highlighting

An example of using the trailing comment `#<<` to highlight lines:

### Code

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````

### Output

```{r tidy=FALSE, eval=FALSE, echo=TRUE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---
name: logos

# A note about logos

### NHS Organisation logo in title slide

The `.title-slide` class in `nhsr.css` looks for a title slide logo using the path to the image relative to your slide files.

### NHS logo on every slide

The NHS logo can be incorporated on every slide using the `use_logo()` function in Garrick Aden-Buie's [xaringanExtra](https://pkg.garrickadenbuie.com/xaringanExtra/#/logo) package, or by following the guidance in his blog post [xaringan Tip: Add A Logo to All of Your Slides](https://www.garrickadenbuie.com/blog/xaringan-tip-logo-all-slides/).

For a more seamless logo experience, you can find this theme and high-resolution NHS logo files built into the [`nhsrtheme` package](https://github.com/nhs-r-community/nhsrtheme#nhs-r-theme-) developed by Tom Jemmett.

.footnote[The **nhsr theme** was designed by [Silvia Canelon](https://silvia.rbind.io) for, and with feedback from, the [NHS-R Community](https://github.com/nhs-r-community), following the [NHS identity guidelines](https://www.england.nhs.uk/nhsidentity/identity-guidelines/).]
