---
title: "Presentation title"
subtitle: "Presentation subtitle"
author: "Author Name"
institute: "NHS Organisation"
date: "Presentation Date"
output:
  xaringan::moon_reader:
    css: 
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "4:3"
    includes:
      after_body: [css/insert-logo.html]
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(nhsrtheme)
library(NHSRdatasets)
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300)

# uncomment the following lines if you want to use the NHS-R theme colours by default
# scale_fill_continuous <- partial(scale_fill_nhs, discrete = FALSE)
# scale_fill_discrete <- partial(scale_fill_nhs, discrete = TRUE)
# scale_colour_continuous <- partial(scale_colour_nhs, discrete = FALSE)
# scale_colour_discrete <- partial(scale_colour_nhs, discrete = TRUE)
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
name: hello
class: middle, center, hide-logo

<img style="border-radius: 50%;" src="https://avatars0.githubusercontent.com/u/53170984?s=200&v=4" width="150px"/>

# NHS-R Community 

## Promoting the use of R in the NHS

--

[`r icon::fa("link")` nhsrcommunity.com](https://nhsrcommunity.com/)<br/>
[`r icon::fa("twitter")` @NHSrCommunity](https://twitter.com/NHSrCommunity)<br/>
[`r icon::fa("github")` @nhs-r-community](https://github.com/nhs-r-community)<br/>
[`r icon::fa("paper-plane")` nhs.rcommunity@nhs.net](mailto:nhs.rcommunity@nhs.net)

???
Hello! My name is NHS-R Community and I'm excited to be here promoting the use of R in the NHS.

---
# About NHS-R Community

The NHS-R community aims to support the learning, application and exploitation of R in the NHS through workshops, video tutorials and providing a platform for discussion and sharing of developing best practice solutions to NHS problems.

With funding support from the Health Foundation’s Advancing Applied Analytics programme (which is aimed at improving analytical capability in support of health and care services.) The Improvement Academy & University of Bradford will lead this initiative  with support from NHS Improvement, NHS Midlands and Lancashire Commissioning Support Unit & NHS Wales Delivery Unit.


.footnote[This excerpt comes from the NHS-R website: https://nhsrcommunity.com/about]


---
class: inverse, middle

# Outline

----

.pull-left[

Outline slides like this one are commonly found in the wild. If they incorporate links they can become a useful "table of contents" for a slide deck.  

Downside is they aren't very memorable. I would encourage a "roadmap" approach to your presentations, using interesting transition slides that let your audience know where you've been and where you're going next.

]<!--end of left-column-->

.pull-right[
.left[
1\. [Making bullet points and emphasizing text](#bulletpoints)

2\. [Tables and quotes](#tables-quotes)

3\. [Line highlighting](#line-highlighting)

4\. [Final slide and contact info](#goodbye)
]
] <!--end of right-column-->

---
name: bulletpoints
# Bullets and text color

--

* first point

--

* second point

--

* third point

--

-----

You can emphasize text with color:

* .blue[Blue]
* .green[Green]
* .pink[Pink]
* .red[Red]
* .warmyellow[Warm Yellow]

--

And make it **bold** or _italicized_ using Markdown:

* .blue[**Bold** or _italicized_]
* .green[**Bold** or _italicized_]
* .pink[**Bold** or _italicized_]
* .red[**Bold** or _italicized_]
* .warmyellow[**Bold** or _italicized_]

---
name: tables-quotes
# Tables and quotes

### Table
.pull-left[

`NHSRDatasets::LOS_model`

Artificially generated hospital data. Fictional patients at 10 fictional hospitals, with `LOS`, `Age` and `Date status` data. 

Data were generated to learn Generalized Linear Models (GLM) concepts, modelling either `Death` or `LOS`.
]

.pull-right[
```{r}
knitr::kable(head(LOS_model), format = 'html')
```
]

--

### Quote

> The NHS-R community aims to support the learning, application and exploitation of R in the NHS through workshops, video tutorials and providing a platform for discussion and sharing of developing best practice solutions to NHS problems.

---
name: line-highlighting

# Code highlighting

`This is what inline code looks like highlighted within text`

Lines within code chunks can be highlighted using the trailing comment `#<<`, as seen below:

### Code

````markdown
`r ''````{r}
NHSRdatasets::LOS_model %>%
  ggplot(aes(x = Age, y = Organisation)) +
  geom_boxplot(aes(fill = Organisation)) +    #<<
  nhsrtheme::scale_fill_nhs("highlights")     #<<
```
````

### Output

```{r eval=FALSE, echo=TRUE}
NHSRdatasets::LOS_model %>%
  ggplot(aes(x = Age, y = Organisation)) +
  geom_boxplot(aes(fill = Organisation)) +    #<<
  nhsrtheme::scale_fill_nhs("highlights")     #<<
```

---
name: goodbye
class: middle, inverse

.pull-left[
# **Thank you!**
<br/>
## NHS-R Community 

### Promoting the use of R in the NHS

### Everywhere, U.K.
]

.pull-right[
.right[
<img style="border-radius: 50%;" src="https://avatars0.githubusercontent.com/u/53170984?s=200&v=4" width="150px"/>


[`r icon::fa("link")` nhsrcommunity.com](https://nhsrcommunity.com/)<br/>
[`r icon::fa("twitter")` @NHSrCommunity](https://twitter.com/NHSrCommunity)<br/>
[`r icon::fa("github")` @nhs-r-community](https://github.com/nhs-r-community)<br/>
[`r icon::fa("paper-plane")` nhs.rcommunity@nhs.net](mailto:nhs.rcommunity@nhs.net)
]
]

???
Thank you for your attention! 
I'm happy to take any questions, and if you'd like to get in touch, I've included my contact information on this slide
